---
title: "DifferentialAnalysis"
output: html_document
date: '2022-11-07'
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
knitr::opts_chunk$set(cache = TRUE, cache.lazy = F)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


### Make the upset plot of top hits at FDR=0.2

```{r, out.width='80%', fig.align='center', eval=T, warning=FALSE}
plotUpsetPlotLimma(limresRegion, 0.2)

```

### Focus on common regulated regions by setting the intersection cutoff to 2


```{r, out.width='80%', fig.align='center', eval=T, warning=FALSE}
plotUpsetPlotLimma(limresRegion, 0.2,intCutoff = 2)

```

### Perform GREAT enrichment for up/down regions at Q-value < 0.2.


```{r diffEnrichAll,  results='hide', message=FALSE, eval=F}
allDiffEnrichmentsGO=greatEnrichmentLimmaAll(limresRegion, 0.2, extended_tss = et, gmt=gmtGO)

```
```{r, eval=F}
allDiffEnrichmentsKEGG$contrast=sub("-.*","", allDiffEnrichmentsKEGG$contrast)
allDiffEnrichmentsGO$contrast=sub("-.*","", allDiffEnrichmentsGO$contrast)
```



```{r, eval=T, echo=F}
kable(topNenrichment(allDiffEnrichmentsGO, p.adjust = 0.1, n=10)[, c(1,2,3,6,7)], row.names = F, digits=5, col.names = c("contrast    ", "direction","term", "p_value", "p_adjust") )
```
#### Comparing Sex specific vs pooled differential methylation tests


```{r, out.width='100%', fig.align='center',eval=T, fig.height=8}
p1=plotUpsetPlotLimma(limresRegion, 0.2,set_size=F)
p2=plotUpsetPlotLimma(limresRegionSexCombined, 0.2, set_size=F)
ggarrange(p1,p2, nrow = 2)
```

### Look at the sex differences in the hippocampus signal in more detail

Pick the regions significant in the joint contrast
```{r}
iHipCont=c(1)
iiHipRegions=which(limresRegionSexCombined$q.value[, iHipCont]<0.05)
length(iiHipRegions)
```

Plot the by sex results for these regions
```{r,  out.width='100%', fig.align='center',eval=T}
iHipCont=c(1,9)
toPlot=limresRegion$t[iiHipRegions, iHipCont]
colnames(toPlot)=c("F", "M")
pres=pheatmap(toPlot, silent = T)
toPlot[limresRegion$q.value[iiHipRegions, iHipCont]>0.2]=NA
pheatmap(toPlot[pres$tree_row$order,], cluster_rows = F, cluster_cols = F, labels_row="")
```

### Look at the overlap between pooled differential genes and genes associated with differential LVs


```{r,echo=T, eval=T}
topLVgenes=getTopGenesEachZ(methres$Z, sigLVs, top = 1000)
totGenes=length(unique(methRegion.table$symbol))

intRes=intersectGeneListsHG(topLVgenes, deGenes, totGenes)
toPlot=(intRes$fold)
toPlot[intRes$fdr>0.05|intRes$fold<1.5]=0
pheatmap(toPlot, main="Overlap between top DEGs and top genes for differential LVs")
```

### Look at the overlap between pooled differential genes and pooled differential DMRs


```{r,echo=T, eval=T}
topDMRgenes=getTopEachContrast(limresRegionSexCombined, top = 1000)

totGenes=length(unique(methRegion.table$symbol))

intRes=intersectGeneListsHG(topDMRgenes, deGenes, totGenes)
toPlot=(intRes$fold)
toPlot[intRes$fdr>0.05|intRes$fold<1.5]=0
pheatmap(toPlot, main="Overlap between top DEGs and top DMR-genes with pooled-sex analysis")
```


### Look at the overlap between pooled differential genes and split differential DMRs


```{r,echo=T, eval=T, fig.height=10}
topDMRgenes=getTopEachContrast(limresRegion, top=1000)

totGenes=length(unique(methRegion.table$symbol))

intRes=intersectGeneListsHG(topDMRgenes, deGenes, totGenes)
toPlot=(intRes$fold)
toPlot[intRes$fdr>0.05|intRes$fold<1.5]=0
pheatmap(toPlot, main="Overlap between top DEGs and top DMR-genes with split-sex analysis")
```