---
title: "RNAdiffExpanded"
output: html_document
date: '2022-11-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```







```{r, eval=T, out.width='80%', fig.align='center'}
plotUpsetPlotLimma(limresRNA, 0.05, top = 10)

```{r, eval=T, out.width='80%', fig.align='center'}
plotUpsetPlotLimma(limresRNASexCombined, 0.05, top = 10)
```

We have so many differentially expressed genes, where is this coming from.

Select a tissue from control and week 8 only and plot the PCA
```{r, eval=T, out.width='80%', fig.align='center'}
ii=which(phenoRNA$tissue=="brown-adipose"&!is.na(phenoRNA$group2))
plotPCAggplotAll(rnaQNforvoom[,ii], grp=phenoRNA$group4[ii], scale=T, do.contour = F, sz=5,do.circle = T)
```
Turn off scaling
```{r, eval=T, out.width='80%', fig.align='center'}
plotPCAggplotAll(rnaQNforvoom[,ii], grp=phenoRNA$group4[ii], scale=F, do.contour = F, sz=5,do.circle = T)
```
Use the raw data, no scaling.
```{r, eval=T, out.width='80%', fig.align='center'}
rnaForPCA=rna
rnaForPCA[is.na(rnaForPCA)]=minval
plotPCAggplotAll(rnaForPCA[,ii], grp=phenoRNA$group4[ii], scale=F, do.contour = F, sz=5,do.circle = T)
```

Select a tissue from control and week 8 only and plot the PCA
```{r, eval=T, out.width='80%', fig.align='center'}
iiH=which(phenoRNA$tissue=="hippocampus"&!is.na(phenoRNA$group2))
plotPCAggplotAll(rnaQNforvoom[,iiH], grp=phenoRNA$group4[iiH], scale=T, do.contour = F, sz=5,do.circle = T)
```
Turn off scaling
```{r, eval=T, out.width='80%', fig.align='center'}
plotPCAggplotAll(rnaQNforvoom[,ii], grp=phenoRNA$group4[ii], scale=F, do.contour = F, sz=5,do.circle = T)
```
Use the raw data, no scaling.
```{r, eval=T, out.width='80%', fig.align='center'}
rnaForPCA=rna
rnaForPCA[is.na(rnaForPCA)]=minval
plotPCAggplotAll(rnaForPCA[,ii], grp=phenoRNA$group4[ii], scale=F, do.contour = F, sz=5,do.circle = T)
```


do enrichments

```{r, eval=F}

 enrichRNA=gmtEnrichmentLimmaAll(limresRNA,0.05, gmt = gmtGOrna, min.sig = 10)
enrichRNA$contrast=sub("\\.w8.*Control", "", enrichRNA$contrast)
```
```{r, eval=T}
topErna=topNenrichment(enrichRNA)
kable(topErna[, c(1:4,7)])
```

```{r, eval=T}
topErna=topNenrichment(enrichRNA, sort = "pval")
kable(topErna[, c(1:4,7)])
```
